\documentclass[11pt,letterpaper,titlepage]{article}
\usepackage[margin=2.54cm]{geometry}
\usepackage{textcomp}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{color}
\usepackage{graphicx}



\title{Resume Critic - Documentation}
\author{David Mulatti, Kyle Petrozzi}
\date{}


\begin{document}
    \maketitle


    \section{Purpose}
        \paragraph{}
        The purpose of this website is to have a place for University of Windsor
        students seeking employment to be able to upload their resume in PDF
        format and have it critiqued by their peers. Users can provide feedback
        in the form of star ratings or comments. The users can upload updated
        resumes as often as they like, and gain new feedback on it. The resumes
        are all public, but only registered users can rate and comment.

    \section{Installation}
        \paragraph{}
        To install the website, simply extract the source code into your
        \emph{public\_html} folder. Then, replace the values in
        \emph{dbaccess.php} with the appropriate information for the database
        you'd like to use, and /assets/recaptcha/secret.php with your own
        secret key provided by Google's reCAPTCHA service (one is provided with
        the site files).
        Lastly, navigate to ``/admin/create\_db.php'' to
        create the database, then navigate to ``/admin/populate\_db.php'' to
        populate the database with four test users, and an admin account.

        \begin{center}
            \begin{tabular}{ | l | l | }
                \multicolumn{2}{c}{Login Info} \\
                \hline
                User Name & Password \\ \hline
                admin & password \\ \hline
                testone & password \\ \hline
                testtwo & password \\ \hline
                testthree & password \\ \hline
                testfour & password \\
                \hline
            \end{tabular}
        \end{center}

        \paragraph{}
        For a working demo, this site is live at
        \href{334.mulatti.com}{334.mulatti.com}.


    \section{Database Design}
        \paragraph{}
        The database for this site contains three tables: users, comments, and
        ratings. The users table stores user info, including uwinid, hashed
        password, full name, rating on their resume, resume upload date,
        description for their resume, and a boolean indicating whether they have
        uploaded a resume or not.

        \paragraph{}
        The comments table stores an auto incrementing comment id, the uwinid of
        the commenter, the uwinid of the user the comment is for, the date of
        the comment, and the comment itself.

        \paragraph{}
        The ratings table is almost identical to the comments table, but does
        not store the date, and is used to store ratings represented as a double
        rather than comments.

    \section{Site Walkthrough}

        \subsection{Design and CSS}
        \paragraph{}
        Bootstrap is used for the design of this site, with the assistance
        of a kickoff template provided by maxdesign \cite{css}. There are
        modifications made to this, located in /assets/css/styles.css.

        \subsection{Admin Control Panel}
        \paragraph{}
        When logged in as admin, an ``Admin'' option appears in the site header
        that will allow one to access the admin control panel. In this, the
        admin can view all of the tables in the database, edit any user, delete
        any comment, drop the database, create the database and populate the
        database with the test data shown above.

        \subsection{Header}
        \paragraph{}
        The header is included in every page on the website. It contains a
        \emph{session\_start()}, the head containing the stylesheet, and jQuery
        and Bootstrap scripts. It also contains the site header itself, which is
        dynamic and changes if a user is logged in or not, and if an admin is
        logged in. Also, if \emph{\$headextra} is set, it will echo that data
        in the head, allowing additional scripts to be loaded on pages that need
        them.

        \paragraph{}
        If a user is not logged in, the ``Upload Resume'' button is replaced
        with a tooltip that appears when it is hovered over, notifying the user
        that they must be logged in to upload a resume. There is also a ``Create
        Account'' and ``Contact Us'' button, along with text fields for a
        user to log in.

        \paragraph{}
        If a user is logged in, the ``Upload Resume'' button becomes active and
        will redirect the user to the upload resume page. The ``Create Account''
        button changes to a ``Edit User Info'' button, and the login fields are
        replaced by a welcome message and logout button. If the user logged in
        is an admin, there is an additional ``Admin'' button added to the
        site header that will redirect to the Admin Control Panel.

        \subsection{Footer}
        \paragraph{}
        The footer is included in every page, and is simply the closing
        $\langle$body$\rangle$ and $\langle$html$\rangle$ tags, as well as a
        centered message including an emoji. The emoji is generated using
        Twitter's \emph{twemoji} plugin \cite{twemoji}.

        \subsection{Create Account}
        \paragraph{}
        Here, there is a is a form that takes a uwinid, password, and full
        name to create a new account. There is also a captcha, provided using
        Google's reCAPTCHA api, to verify that the person signing up for an
        account is indeed human. The form uses the jQuery Validation plugin
        \cite{validate} to validate all the fields, including AJAX calls to the
        database to ensure that a username is not taken. It will also ensure
        that the password is at least 8 characters long, and that the full name
        only has alphanumeric characters in it.

        \paragraph{}
        On submission, all fields are sent as POST variables to
        \emph{createaccount\_go.php} which will insert a new user into the
        database. The password is hashed using the \emph{password\_hash()}
        function, provided by ircmaxwell \cite{password}.

        \subsection{Login and Logout}
        \paragraph{}
        The login.php is relatively simple. It compares the password sent within
        the form to the hashed password stored in the database associated with
        the appropriate uwinid, using the \emph{password\_verify()} function.
        If it matches, it sets the \emph{logged\_in}
        session variable to 1, and then redirects back to the index page. It
        also checks if the user logging in is the admin, and if so, changes the
        session variable to 3. It also has an error page if the wrong username
        or password is entered.

        \subsection{Edit User}
        \paragraph{}
        The edit user link appears in the header whenever a user is logged in. A
        user can then edit their Full Name or their password. If an admin is
        logged in, then the edit user page is extended, allowing the admin to
        change many more options for any user they wish.

        \subsection{Resume Upload}
        \paragraph{}
        This page is used to upload/edit your own resume page. If you are logged
        in you can add or update a resume and description. If you already have a
        resume uploaded, it shows it to you as an embedded object, and auto
        fills the description with your last description used. When you press
        the upload button it redirects to upload.php. This will check if the
        file uploaded is a application/pdf MIME type, if it comes from the POST
        function, and finally if it is not too large of a file. If all of these
        checks pass, then it saves the file as \emph{uwinid}.pdf, \emph{uwinid}
        being the username of the current user, in a ``resume'' folder located
        in the site root directory. It also updates the upload date, the
        \emph{has\_uploaded} boolean, and the description columns within the
        database to corresponding to the user who uploaded. It also will add a
        comment to the resume, notifying that a new resume has been uploaded. It
        then redirects back to the resume viewer page on success, and to an
        error page if something has failed.

        \subsection{Resume Viewer}
        \paragraph{}
        When a name on the homepage is clicked, the user is brought to a page
        which displays the resume as an embedded object on the left, and the
        description, upload date, and comments on the resume on the right. Above
        the resume there is a current star rating of the resume, gathered by
        what the users have voted.

        \paragraph{}
        If the user is logged in, below the comments there is a textarea to add
        their own comment, and an option to rate the resume out of five stars.
        The star rating system is powered by a jQuery plugin for bootstrap made
        by GitHub user \emph{kartik-v} \cite{stars}.

        \subsection{Contact Us}
        \paragraph{}
        The ``Contact Us'' page displays our names, some information about
        ourselves, and our email addresses. There is also a link to the GitHub
        page that our code is available on, and a form including a TinyMCE
        \cite{tinymce} editor to send an email directly to us using the PHP
        \emph{mail()} function. In addition, if a user is logged in, their
        name and email address are automatically filled in.

        \paragraph{}
        On submission of the contact form, the user is redirected to
        \emph{contact\_go.php} which takes the POST variables from the form,
        validates the captcha, and processes the message given from the TinyMCE
        editor through XSLT to strip out everything that isn't a
        $\langle$div$\rangle$, $\langle$strong$\rangle$, or $\langle$em$\rangle$
        tag. In addition, any $\langle$a$\rangle$ tag is stripped if the
        URL is not prefixed with ``334.mulatti.com''.

    \section{Security}
    \paragraph{}
    Every database query that requires user input is made using prepared
    statements and the mysqli extension. All form data is verified using
    jQuery validate, and again by checking the input in the PHP code that
    processes it.

    \paragraph{}
    The admin pages can only be accessed when an admin is logged in, and will
    \emph{die()} otherwise. The \emph{create\_db.php} and
    \emph{populate\_db.php} pages do not have this restriction, so that it is
    easy to set up the database  when installing the site. However, if these try
    to be ran a second time, nothing  will happen since the queries to create
    the tables have the ``IF NOT EXISTS'' constraint,  and
    \emph{populate\_db.php} will throw errors because it is trying to  create
    duplicate entries. Thus, restricting these access of these two pages only
    complicates the installation of the website.



    \newpage
    \begin{thebibliography}{9}

        \bibitem{css}
          russmaxdesign,
          \emph{Bootstrap Kickoff Template}\\
          Available at:
          \href{https://github.com/russmaxdesign/01-bootstrap-kickoff-template}
               {https://github.com/russmaxdesign/01-bootstrap-kickoff-template}

        \bibitem{twemoji}
        Twitter,
        \emph{Twitter Emoji For Everyone}\\
        Available at: \href{https://github.com/twitter/twemoji}
                        {https://github.com/twitter/twemoji}

        \bibitem{validate}
        jQuery Validation\\
        Available at: \href{http://jqueryvalidation.org/}
                           {http://jqueryvalidation.org/}

        \bibitem{password}
        ircmaxwell,
        \emph{password\_compat}\\
        Available at: \href{https://github.com/ircmaxell/password_compat}
                           {https://github.com/ircmaxell/password\_compat}

       \bibitem{stars}
       kartik-v,
       \emph{bootstrap-star-rating}\\
       Available at: \href{https://github.com/kartik-v/bootstrap-star-rating}
                          {https://github.com/kartik-v/bootstrap-star-rating}

       \bibitem{tinymce}
       TinyMCE\\
       Available at: \href{https://www.tinymce.com/}
                          {https://www.tinymce.com/}

    \end{thebibliography}



\end{document}
